Supplementary Materials: Probing the Deuteron at Very Large Internal Momenta

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/MARKED/ms_revised.tex
updated

$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}. Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance

@@

  Insets: Blowup of the subfigures below $p_{\mathrm{r}}=$0.7 GeV/c.}

@@

to improve the statistics. \\

>>>>

$\Lambda^{2}\sim 0.8-1 $ (GeV/c)$^{2}$ \cite{Sargsian_2001}, this results in an additional $1/Q^{4}$ suppression as compared to the quasi-elastic contribution. Note that other meson exchange contributions that take place before the virtual photon interaction are included in the definition of the ground state wave function of the deuteron. IC can be suppressed kinematically by selecting $x_{\mathrm{Bj}}>1$, where one probes the lower energy ($\omega$) part of the deuteron quasi-elastic peak which is maximally away from the inelastic resonance

@@

  Insets: Blowup of the subfigures for $p_{\mathrm{r}}\leq$0.7 GeV/c.}

@@

to improve the statistics. Furthermore, the new data set is ideal for testing fully relativistic deuteron models based on light-front or covariant formalisms.
In this respect the current effective field theories (EFT) based models \cite{Reinert_EFT2018} are non-relativistic and might not have direct relevance to our data. \\

### 2020-11-23 MY_PUBLICATIONS/PRL/FINAL_DRAFT/PRL_Submission/prl_response_2/reply_2/supplemental/supplemental.tex
updated

\includegraphics[scale=0.3]{Pr_and_Ps_35deg.png}
\includegraphics[scale=0.3]{Pr_and_Ps_45deg.png}

@@

\includegraphics[scale=0.3]{RedXsec_overlap.png}
\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings.}

>>>>

\includegraphics[scale=0.29]{Pr_and_Ps_35deg.png}
\includegraphics[scale=0.29]{Pr_and_Ps_45deg.png}

@@

\includegraphics[scale=0.23]{RedXsec_overlap.png}
\caption{Reduced cross section overlap region between the 580 and 750 MeV/c settings. The 750 MeV/c setting has been offset (right) by +0.01 GeV/c for ease of comparison.}
